---
output: github_document
---


```{r message=FALSE}
library(reticulate)
library(tidyverse)
library(fs)
```



```{r}
reticulate::py_discover_config()
# virtualenv choice has been hardwired by setting RETICULATE_PYTHON_ENV in .Renviron
#reticulate::use_virtualenv("/opt/venv/keras-rl")
```

We let python do all the actual work: (We could alternately call the python functions directly via reticulate or embed the python in a `python` code chunk in the notebook, which would let us edit the parameters more easily here.)

`fishing_discrete.py` sets an action space of 100 actions, each corresponding to the choice of harvest quota (such that `quota = action / n_actions * K`):

```{r eval=FALSE}
fs::file_delete("fishing-100.csv")
reticulate::source_python("fishing_discrete.py")
```


Let's plot the results (in R)

```{r}
fishing <- read_csv("../fishing-100.csv", 
                    col_names = c("time", "state", "harvest", "action"))

d <- max(fishing$time)
n <-dim(fishing)[1] / d

fishing$rep <- as.character(vapply(1:n, rep, integer(d), d))

## Reward is calculated as net (cumulative) reward without any discounting (gamma = 1),
## not the (discounted) net present value typically used in optimal control
gamma <- 0.99
price <- 1.0
fishing <- fishing %>% 
  group_by(rep) %>% 
  mutate(reward = cumsum(price * harvest), 
         npv = cumsum(price * harvest * gamma^time))

## this matches the rewards reported by `dqn.test`:
fishing %>% summarize(max(reward))
```

Some plots, focusing on the early period to make the pattern more visible:


```{r}
fishing %>% 
  filter(time < 100) %>%
  ggplot(aes(time, state, col = rep)) + geom_line() + facet_wrap(~rep)
```

```{r}
fishing %>% 
  filter(time < 150) %>%
  ggplot(aes(time, harvest, col = rep)) + geom_line() + facet_wrap(~rep)
```

```{r}
fishing %>% 
  filter(time < 30) %>%
  ggplot(aes(time, action, col = rep)) + geom_point() + facet_wrap(~rep)
```

```{r}
fishing %>% 
  filter(time < 30) %>%
  ggplot(aes(time, reward, col = rep)) + geom_point() + facet_wrap(~rep)

```
